---
title: "McSweeney_Command Line"
author: "Danny McSweeney"
date: "5/11/2020"
output: html_document
---
##I tried to insert ```{bash...} chunks into this file, but they would not insert. I restarted RStudio, and the option to insert a chunk disappeared and was replaced by a simple R button.


```{r}
names(knitr::knit_engines$get())
```



#View the current directory
```{r}
pwd
```


#See what's in the directory
```{r}
ls -l
```


#MAke a new directory
```{r}
mkdir MYDRAFTS
```


#Enter the directory
```{r}
cd MYDRAFTS
```


#See what's in the directory
```{r}
ls -a
```


#Make a new file use the nano text file maker
```{r}
nano test1
```


#Navigating around the directories and seeing what's in them
```{r}
cd
cd MYDRAFTS
ls
ls -a
cd
```


#Make a new directory
```{r}
mkdir MYDRAFTS2
cd
ls
pwd
cd MYDRAFTS
pwd
```


#Remove a directory
```{r}
rm -r MYDRAFTS
ls -a
home/ --
cd TERMFILES
mkdir CASK
ls
rmdir CASK
ls
cd
```


#concatenate files
```{r}
cat .tester5
cd TERMFILES
cat TERMFILES
cat TERMFILES tester3 > temp1
cd TERMFILES2
cat TERMFILES2 tester4 > temp1
```



#Copy files
```{r}
cp Tester temp1
```


#Move files
```{r}
mv temp1 temp2
```


#Look at top # of rows in file
```{r}
head -2 temp2
```


#Look at bottom # of rows in file
```{r}
tail -1 temp1
```



```{r}
grep see temp2
who
```


